Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-08-03 revision/responseToreviewers.tex

\title{Reply to reviewer concerning submission APAC$\_$2018$\_$311 'Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization' in Applied Acoustics.}

\begin{document}

\maketitle

As a preamble, we would like to thank the editor and the reviewer for the comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to the reviewer's comments, with references to the revised manuscript where appropriate.

@@

An interesting approach to estimate the sound level of road traffic in an urban sound environment composed of a mixture of sound sources is presented in the reviewed paper.

The work is well planned and structured. It has an adequate length and the results are interesting.

I only have some minor indications that I think they can improve a little bit this paper.

\begin{enumerate}
\item The use of the letter beta should be clarified because its use in expressions (5, 8a, 8b and 8c) and in lines 104-105, seems not to be the same that its use in expressions (4a, 4b y 4c) or, for example, in tables 3 and 4.\\
$\rightarrow$ Done: the $\beta$ value in 4 is the same that in the expressions 5 and 8. This has been precised: 'Thus, the choice of the $\beta$-divergence in the equation affects how the matrix $\mathbf{H}$ is updated.' (section 2.1).

@@

\item In relation with table 4, it may be appropriate that it includes some more complete representation or table of results, for the reader interested in analyzing in more detail the effects that the different variables analyzed may have on errors. For example, one in which, varying one of the variables analyzed, the others remain constant.

$\rightarrow$ We added a part, between the lines 610 and 642, dedicated to this where the evolution of the cost functions and the $MAE$ errors are displayed according to the iteration (section 5, Figure 10) and the evolution of the error according to $K$ and $w_t$ are exposed (Figure 11).

@@

\item References: The bibliographic revision is good, but maybe, some references can be improved.

For example, reference (3), because it is a congress, not a peer reviewed paper. Only as an example, you can considerer the references: https://doi.org/10.1016/j.apacoust.2010.06.010 and https://doi.org/10.1016/j.scitotenv.2011.10.018 .

In line 67, it is indicated that “Many works…” but only two references are included. Author may considerer others, for example: 
http://dx.doi.org/10.1016/j.apacoust.2016.05.020 and https://doi.org/10.2478/v10168-012-0054-z

At the end of the lines 30-31, it is possible that some general references are needed. For example, 
https://doi.org/10.3813/AAA.918456 and http://dx.doi.org/10.1016/j.apacoust.2016.04.018.\\
$\rightarrow$ Done, some references, suggested by the reviewers, have been added to the different locations indicated.

\item Moreover, there are references that just have been submitted to publication. \\
$\rightarrow$ Done for one reference, the other is in revision.

### 2018-08-03 revision/articleNmfTrafficSimScene2018_v2.tex
Re-submission before acceptation

Different cut-off frequencies have been chosen such as $f_c \in \lbrace$500, 1k, 2k, 5k, 10k, 20k$\rbrace$ Hz. The experimental factors related to this estimator are summarized in Table \ref{tab:experimental_factorsFilter}.

@@

A $\mathbf{K}$-means clustering algorithm is applied to those elements to reduce these dimensions to $\mathbf{K} \in \lbrace$25, 50, 100, 200$\rbrace$ in order to avoid redundant information and decrease the computation time. The resulting $\mathbf{K}$ cluster centroids are taken as the elements of $\mathbf{W}$. Each basis of $\mathbf{W}$ is then normalized as $ \Vert \mathbf{w} \Vert = 1$ where $\Vert \bullet \Vert$ is the $\ell_1$ norm. Table \ref{tab:experimental_factorsNMF} summarizes the different modalities of the two experimental factors ($\mathbf{K}$ and $\mathbf{w_t}$).

@@

NMF is performed for 3 $\beta$-divergences: $\beta$ = 2 (Euclidean distance), $\beta$ = 1 (Kullback-Leibler divergence) and $\beta = 0$ (Itakura-Sa\"ito divergence). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed in a logarithmic scale through a third octave band representation that reduces the high frequency predominance where the traffic component is absent. In addition, as the number of frequency bins is reduced ($F$ = 29), the computation time is reduced too. 400 iterations are performed to get a stabilized results. For SEM-NMF, the number of elements in $\mathbf{W_r}$ is set to $J = 2$. For hard thresholding, the threshold value, $\mathbf{t_h}$ is set between 0.30 and 0.60 with a 0.01 increment.
Each unique association of modalities between each experimental factor forms an experimental setting. For the filter estimator, 24 settings are computed (4 $\times$ 6). For SUP and SEM-NMF, 192 settings are computed (4 $\times$ 2 $\times$ 2 $\times$ 4 $\times$ 3). Finally, for TI-NMF, the number of settings is much higher (2976) due to the higher cardinality of the set of threshold values (4 $\times$ 1 $\times$ 2 $\times$ 4  $\times$ 3 $\times$ 31).
The experimental factors and their different modalities are displayed in Tables \ref{tab:experimental_factorsFilter} and \ref{tab:experimental_factorsNMF}.

@@

\begin{table*}[t]
\caption{Experimental factors and their modalities for the frequency low-pass filter baseline estimator.}
\centering
\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\hline
    \textbf{\begin{tabular}[c]{@{}l@{}}experimental \\ factors\end{tabular}} & \textbf{modalities} & \begin{tabular}[c]{@{}C{2cm}@{}}\textbf{number of}\\ \textbf{modalities}\end{tabular}\\ \toprule
\end{tabularx}

\begin{tabularx}{17.5cm}{L{3cm}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}C{2cm}@{}}
    \textbf{sound environment} & \begin{tabular}[c]{@{}c@{}}park\\ 'P'\end{tabular} & \begin{tabular}[c]{@{}c@{}}quiet street\\ 'Q'\end{tabular} & \begin{tabular}[c]{@{}c@{}}noisy street\\ 'N' \end{tabular}& \begin{tabular}[c]{@{}c@{}}very noisy street\\ 'vN'\end{tabular} & 4\\
\end{tabularx}

\begin{tabularx}{17.5cm}{L{3cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}C{2cm}@{}}
\rowcolor[HTML]{C0C0C0}
   $\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 &  5 & 10 & 20 & 6\\
   \bottomrule
\end{tabularx}

\label{tab:experimental_factorsFilter}
\end{table*}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}C{2cm}@{}}
    \textbf{sound environment} & \begin{tabular}[c]{@{}c@{}}park\\ 'P'\end{tabular} & \begin{tabular}[c]{@{}c@{}}quiet street\\ 'Q'\end{tabular} & \begin{tabular}[c]{@{}c@{}}noisy street\\ 'N' \end{tabular}& \begin{tabular}[c]{@{}c@{}}very noisy street\\ 'vN'\end{tabular} & 4\\
\end{tabularx}

\begin{tabularx}{17.5cm}{L{3cm}@{}C{4cm}@{}@{}@{}C{4cm}@{}@{}C{4cm}@{}C{2cm}@{}}
	\rowcolor[HTML]{C0C0C0}
  \textbf{method} & SUP NMF & SEM NMF & TI NMF & 3\\
\end{tabularx}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\rowcolor[HTML]{C0C0C0}
   hard threshold $\mathbf{t_h}$ & from 0.30 to 0.60 with a 0.01 step & 31\\
   \bottomrule
\end{tabularx}
\label{tab:experimental_factorsNMF}
\end{table*}

@@

Finally, TI-NMF presents the most performing results, except in the \textit{park} environment ($MAE$ = 2.95 dB). In this sound environment, with the threshold value $t_h$ = 0.32, the traffic dictionary is composed, on average, of 136 elements.
By increasing this value, it would be possible to put aside the spectra furthest away of the traffic elements and then decrease the error. For the rest of the sound environments, TI-NMF has the lowest errors. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). With on average 198 elements in $\mathbf{W}_{traffic}$, almost all the elements present in $\mathbf{W'}$ can be considered as traffic elements.

Considering a unique dictionary fitted to the sound scene under evaluation thus makes TI-NMF very effective when traffic is predominant, while the thresholding step make it possible to discards the elements of the dictionary that deviate too much when the traffic is less present.

@@

Further analyses are required to extend the proposed method to other sound sources, such as birds or voices sounds, which can conveniently be done by replacing or adding elements in the dictionary. This utilization would be useful in the context of muti-source noise mapping that is gaining interest \cite{aumond2017Probabilistic, aletta2015soundscape}. Finally, the parameters selected in this study are valid for this evaluation corpus. Further analyses on various corpus of sound scenes are needed to evaluate the robustness of the method and select the most relevant approaches for specific sound environments (predominance of water or industrial sounds, rural environments \dots).

>>>>

Different cut-off frequencies have been chosen such as $f_c \in \lbrace$500, 1k, 2k, 5k, 10k, 20k$\rbrace$ Hz. The experimental factors related to this estimator are summarized in Table \ref{tab:experimental_factors}.

@@

A $\mathbf{K}$-means clustering algorithm is applied to those elements to reduce these dimensions to $\mathbf{K} \in \lbrace$25, 50, 100, 200$\rbrace$ in order to avoid redundant information and decrease the computation time. The resulting $\mathbf{K}$ cluster centroids are taken as the elements of $\mathbf{W}$. Each basis of $\mathbf{W}$ is then normalized as $ \Vert \mathbf{w} \Vert = 1$ where $\Vert \bullet \Vert$ is the $\ell_1$ norm. Table \ref{tab:experimental_factors} summarizes the different modalities of the two experimental factors ($\mathbf{K}$ and $\mathbf{w_t}$).

@@

NMF is performed for 3 $\beta$-divergences: $\beta$ = 2 (Euclidean distance), $\beta$ = 1 (Kullback-Leibler divergence) and $\beta = 0$ (Itakura-Sa\"ito divergence). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed in a logarithmic scale through a third octave band representation that reduces the high frequency predominance where the traffic component is absent. In addition, as the number of frequency bins is reduced ($F$ = 29), the computation time is reduced too. 400 iterations are performed to get a stabilized results. For SEM-NMF, the number of elements in $\mathbf{W_r}$ is set to $J = 2$. For hard thresholding, the threshold value, $\mathbf{t_h}$ is set between 0.30 and 0.60 with a 0.01 increment.
Each unique association of modalities between each experimental factor forms an experimental setting. For the filter estimator, 24 settings are computed (4 $\times$ 6). For SUP and SEM-NMF, 192 settings are computed (4 $\times$ 2 $\times$ 2 $\times$ 4 $\times$ 3). Finally, for TI-NMF, the number of settings is much higher (2976) due to the higher cardinality of the set of threshold values (4 $\times$ 1 $\times$ 2 $\times$ 4  $\times$ 3 $\times$ 31).
The experimental factors and their different modalities are displayed in Table \ref{tab:experimental_factors}.

@@

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}C{2cm}@{}}
	\rowcolor[HTML]{C0C0C0}
    \textbf{sound environment} & \begin{tabular}[c]{@{}c@{}}park\\ 'P'\end{tabular} & \begin{tabular}[c]{@{}c@{}}quiet street\\ 'Q'\end{tabular} & \begin{tabular}[c]{@{}c@{}}noisy street\\ 'N' \end{tabular}& \begin{tabular}[c]{@{}c@{}}very noisy street\\ 'vN'\end{tabular} & 4\\
\end{tabularx}

\begin{tabularx}{17.5cm}{L{3cm}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}@{}C{3cm}@{}C{2cm}@{}}
  \textbf{method} &  LP Filter & SUP NMF & SEM NMF & TI NMF & 4\\
\end{tabularx}

\begin{tabularx}{17.5cm}{L{3cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}@{}C{2cm}@{}C{2cm}@{}}
\rowcolor[HTML]{C0C0C0}
   $\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 &  5 & 10 & 20 & 6\\
\end{tabularx}

@@

\begin{tabularx}{17.5cm}{L{3cm}@{}C{12cm}@{}C{2cm}@{}}
	\rowcolor[HTML]{C0C0C0}
   hard threshold $\mathbf{t_h}$ & from 0.30 to 0.60 with a 0.01 step & 31\\
   \bottomrule
\end{tabularx}
\label{tab:experimental_factors}
\end{table*}

@@

Finally, TI-NMF presents the most performing results, except in the \textit{park} environment ($MAE$ = 2.95 dB). In this sound environment, with the threshold value $t_h$ = 0.32, the traffic dictionary is composed, on average, of 136 elements.
By increasing this value, it would be possible to put aside the spectra furthest away of the traffic elements and then decrease the error. For the rest of the sound environments, TI-NMF has the lowest errors. For very noisy environment the error is even very low ($MAE=$ 0.28 dB). With on average 198 elements in $\mathbf{W}_{traffic}$, almost all the elements present in $\mathbf{W'}$ can be considered as traffic elements. 
Considering a unique dictionary fitted to the sound scene under evaluation thus makes TI-NMF very effective when traffic is predominant, while the thresholding step makes it possible to discard the elements of the dictionary that deviate too much when the traffic is less present.

\begin{figure*}[t!]
\centering
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionK_AA.pdf}
\caption{Influence of the experimental factor $\mathbf{K}$ (TI-NMF, $w_t$ = 0.5 s, $\beta$ = 2, $t_h$ = 0.32, 400 iterations).} \label{fig:grafic_K}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\linewidth]{./figures/evolutionWt_AA.pdf}
\caption{Influence of the experimental factor $\mathbf{w_t}$ (TI-NMF, $K$ = 200 s, $\beta$ = 2, $t_h$ = 0.32, 400 iterations).} \label{fig:grafic_wt}
\end{subfigure}
\caption{Influence of the number of elements $\mathbf{K}$ (\subref{fig:grafic_K}) and the temporal frame $\mathbf{w_t}$ (\subref{fig:grafic_wt}) on the $mMAE$ error with the best TI-NMF obtained in Table \ref{tab:results}.} \label{fig:grafic_K_wt}
\end{figure*}

To better understand the behavior of TI-NMF, the evolution of the normalized cost function ($D(\mathbf{V}\Vert \mathbf{WH})/(F\times N)$ as the duration of each audio sample is different) and the error $MAE$ as the function of the number of iterations are displayed for each sound environment in Figure \ref{fig:grafic_cost_mae}. For each sound environment, the cost function is very low after 400 iterations, meaning that $\mathbf{WH}$ approximates correctly $\mathbf{V}$. However, even if the convergence is not reached (Figure \ref{fig:grafic_cost}), the traffic error reconstruction is constant after the \nth{200} iteration (Figure \ref{fig:grafic_mae}), which means that the updates of $\mathbf{W}$ and $\mathbf{H}$ are mostly dedicated to the interfering sound sources. Also, even if the cost function is higher for the \textit{very noisy street} than the \textit{park}, the traffic sound level estimation is better in the \textit{very noisy street} sound environment due to the higher presence of this component in it.

Finally, the influence of the number of elements $\mathbf{K}$ in $\mathbf{W}$ and the size of the temporal frame $\mathbf{w_t}$ on the $mMAE$ error made with TI-NMF, with the other experimental factors keep constant, are summarized in Figure \ref{fig:grafic_K_wt}. 
Naturally, the traffic error reconstruction decreases, with the increase of the number of basis in $\mathbf{W}$, as it allows more basis to describe the traffic sound source. If this improvement is major between 25 and 100 elements, its influence decreases between 100 and 200 elements suggesting that the increase of the size of $\mathbf{K}$ will not improve significantly the quality of the estimation. The temporal frame $\mathbf{w_t}$ is a less influential parameter for TI-NMF. As the matrices are updates at each iteration, it makes sense that the variations in the spectra shape in $\mathbf{W_0}$, due to this experimental factor, will disappear after a set of iterations.

@@

Further analyses are required to extend the proposed method to other sound sources, such as birds or voices sounds, which can conveniently be done by replacing or adding elements in the dictionary. This utilization would be useful in the context of muti-source noise mapping that is gaining interest \cite{aumond2018probabilistic, aletta2015soundscape}. Finally, the parameters selected in this study are valid for this evaluation corpus. Further analyses on various corpus of sound scenes are needed to evaluate the robustness of the method and select the most relevant approaches for specific sound environments (predominance of water or industrial sounds, rural environments\dots).
